One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-01-12 Zhiyu.tex
Jan12 PRE format, tex

Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant. If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t). 
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation of radius R defined in Eq.\ref{eq:def_of_R}}
\label{fig:Breathingfrequency1}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_1_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_2_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E.}
\label{fig:LLEdistribution1}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
\caption{``hot". top(bottom): default(modified)}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_parula1_screenshot.png}
\caption{``parula". top(bottom): default(modified)}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone1_screenshot.png}
\caption{``bone". top(bottom): default(modified)}
\end{figure}

>>>>

Since the number of particles we use in the Molecular Dynamics simulation is limited (usually 5 to 20), the random noise is significant. If we start with a state whose configuration in phase-space is an ellipse slightly deviated from circle, the oscillating amplitude will be too small to be distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x, zero p) and observe the oscillation of R(t). 
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.32]{D:/matlab2016/MolecularDynamics/figure/latexpic/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behaviour of radius R(t) defined in Eq.\ref{eq:def_of_R}. The breathing frequency is measured by taking Fourier transformation of R(t).}
\label{fig:Breathingfrequency1}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot1_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_hot2_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E.``hot". top(bottom):modified(reversed)}
\end{figure}
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone1_screenshot.png}
\includegraphics[scale=0.4]{D:/matlab2016/MolecularDynamics/figure/latexpic/LLEdistribution_1_11_pre_bone2_screenshot.png}
\caption{``bone". top(bottom):modified(reversed)}
\end{figure}
